### 2014-07-24 Projects/Spartanburg_2014/Report/Spartanburg_2014.tex
Spartanburg: Cleanup plot dirs and add report files

\headerB{
Delco 2014
}

@@

\subsection{Construction}
\label{sec:Construction}
The building was composed of concrete walls, as shown in Fig.~\ref{fig:EL_Logo_Example}.

\begin{figure}[!ht]
\includegraphics[width=2in]{../Figures/el_logo_small}
\caption{NIST Engineering Laboratory}
\label{fig:EL_Logo_Example}
\end{figure}

@@

\begin{figure}[!ht]
\includegraphics[width=6in]{../Figures/Script_Figures/HOSE_DNXAXX_BDP_A8}
\caption{Velocity at exterior Door C\_West, Test HOSE\_DNXAXX}
\label{fig:HOSE_DNXAXX_BDP_A8}
\end{figure}

\begin{figure}[!ht]
\includegraphics[width=6in]{../Figures/Script_Figures/HOSE_DNXAXX_BDP_A9}
\caption{Velocity at exterior Door C\_East, Test HOSE\_DNXAXX}
\label{fig:HOSE_DNXAXX_BDP_A9}
\end{figure}

\begin{figure}[!ht]
\includegraphics[width=6in]{../Figures/Script_Figures/HOSE_DNXAXX_HOSE}
\caption{Hose pressure, Test HOSE\_DNXAXX}
\label{fig:HOSE_DNXAXX_HOSE}
\end{figure}

@@

\begin{figure}[!ht]
\includegraphics[width=6in]{../Figures/Script_Figures/HOSE_DNXOXF_BDP_A8}
\caption{Velocity at exterior Door C\_West, Test HOSE\_DNXOXF}
\label{fig:HOSE_DNXOXF_BDP_A8}
\end{figure}

\begin{figure}[!ht]
\includegraphics[width=6in]{../Figures/Script_Figures/HOSE_DNXOXF_BDP_A9}
\caption{Velocity at exterior Door C\_East, Test HOSE\_DNXOXF}
\label{fig:HOSE_DNXOXF_BDP_A9}
\end{figure}

\begin{figure}[!ht]
\includegraphics[width=6in]{../Figures/Script_Figures/HOSE_DNXOXF_HOSE}
\caption{Hose pressure, Test HOSE\_DNXOXF}
\label{fig:HOSE_DNXOXF_HOSE}
\end{figure}

\subsection{DSXAXF}

\begin{figure}[!ht]
\includegraphics[width=6in]{../Figures/Script_Figures/HOSE_DSXAXF_BDP_A7}
\caption{Velocity at exterior Door A, Test HOSE\_DSXAXF}
\label{fig:HOSE_DSXAXF_BDP_A7}
\end{figure}

\begin{figure}[!ht]
\includegraphics[width=6in]{../Figures/Script_Figures/HOSE_DSXAXF_BDP_A8}
\caption{Velocity at exterior Door C\_West, Test HOSE\_DSXAXF}
\label{fig:HOSE_DSXAXF_BDP_A8}
\end{figure}

\begin{figure}[!ht]
\includegraphics[width=6in]{../Figures/Script_Figures/HOSE_DSXAXF_BDP_A9}
\caption{Velocity at exterior Door C\_East, Test HOSE\_DSXAXF}
\label{fig:HOSE_DSXAXF_BDP_A9}
\end{figure}

\begin{figure}[!ht]
\includegraphics[width=6in]{../Figures/Script_Figures/HOSE_DSXAXF_HOSE}
\caption{Hose pressure, Test HOSE\_DSXAXF}
\label{fig:HOSE_DSXAXF_HOSE}
\end{figure}

\subsection{DSXOXF}

\begin{figure}[!ht]
\includegraphics[width=6in]{../Figures/Script_Figures/HOSE_DSXOXF_BDP_A7}
\caption{Velocity at exterior Door A, Test HOSE\_DSXOXF}
\label{fig:HOSE_DSXOXF_BDP_A7}
\end{figure}

\begin{figure}[!ht]
\includegraphics[width=6in]{../Figures/Script_Figures/HOSE_DSXOXF_BDP_A8}
\caption{Velocity at exterior Door C\_West, Test HOSE\_DSXOXF}
\label{fig:HOSE_DSXOXF_BDP_A8}
\end{figure}

\begin{figure}[!ht]
\includegraphics[width=6in]{../Figures/Script_Figures/HOSE_DSXOXF_BDP_A9}
\caption{Velocity at exterior Door C\_East, Test HOSE\_DSXOXF}
\label{fig:HOSE_DSXOXF_BDP_A9}
\end{figure}

\begin{figure}[!ht]
\includegraphics[width=6in]{../Figures/Script_Figures/HOSE_DSXOXF_HOSE}
\caption{Hose pressure, Test HOSE\_DSXOXF}
\label{fig:HOSE_DSXOXF_HOSE}
\end{figure}

\subsection{IXAOXX}

\begin{figure}[!ht]
\includegraphics[width=6in]{../Figures/Script_Figures/HOSE_IXAOXX_BDP_A6}
\caption{Velocity at interior Door CD, Test HOSE\_IXAOXX}
\label{fig:HOSE_IXAOXX_BDP_A6}
\end{figure}

\begin{figure}[!ht]
\includegraphics[width=6in]{../Figures/Script_Figures/HOSE_IXAOXX_BDP_A7}
\caption{Velocity at exterior Door A, Test HOSE\_IXAOXX}
\label{fig:HOSE_IXAOXX_BDP_A7}
\end{figure}

\begin{figure}[!ht]
\includegraphics[width=6in]{../Figures/Script_Figures/HOSE_IXAOXX_BDP_A8}
\caption{Velocity at exterior Door C\_West, Test HOSE\_IXAOXX}
\label{fig:HOSE_IXAOXX_BDP_A8}
\end{figure}

\begin{figure}[!ht]
\includegraphics[width=6in]{../Figures/Script_Figures/HOSE_IXAOXX_BDP_A9}
\caption{Velocity at exterior Door C\_East, Test HOSE\_IXAOXX}
\label{fig:HOSE_IXAOXX_BDP_A9}
\end{figure}

\begin{figure}[!ht]
\includegraphics[width=6in]{../Figures/Script_Figures/HOSE_IXAOXX_HOSE}
\caption{Hose pressure, Test HOSE\_IXAOXX}
\label{fig:HOSE_IXAOXX_HOSE}
\end{figure}

\subsection{IXXAXX}

\begin{figure}[!ht]
\includegraphics[width=6in]{../Figures/Script_Figures/HOSE_IXXAXX_BDP_A6}
\caption{Velocity at interior Door CD, Test HOSE\_IXXAXX}
\label{fig:HOSE_IXXAXX_BDP_A6}
\end{figure}

\begin{figure}[!ht]
\includegraphics[width=6in]{../Figures/Script_Figures/HOSE_IXXAXX_BDP_A7}
\caption{Velocity at exterior Door A, Test HOSE\_IXXAXX}
\label{fig:HOSE_IXXAXX_BDP_A7}
\end{figure}

\begin{figure}[!ht]
\includegraphics[width=6in]{../Figures/Script_Figures/HOSE_IXXAXX_BDP_A8}
\caption{Velocity at exterior Door C\_West, Test HOSE\_IXXAXX}
\label{fig:HOSE_IXXAXX_BDP_A8}
\end{figure}

\begin{figure}[!ht]
\includegraphics[width=6in]{../Figures/Script_Figures/HOSE_IXXAXX_BDP_A9}
\caption{Velocity at exterior Door C\_East, Test HOSE\_IXXAXX}
\label{fig:HOSE_IXXAXX_BDP_A9}
\end{figure}

\begin{figure}[!ht]
\includegraphics[width=6in]{../Figures/Script_Figures/HOSE_IXXAXX_HOSE}
\caption{Hose pressure, Test HOSE\_IXXAXX}
\label{fig:HOSE_IXXAXX_HOSE}
\end{figure}

\section{Fire Tests}

\subsection{FIRE\_FA2S1C1NCX1\_1}

\begin{figure}[!ht]
\includegraphics[width=6in]{../Figures/Script_Figures/FIRE_FA2S1C1NCX1_1_BDP_A7}
\caption{Velocity at exterior Door A, Test FIRE\_FA2S1C1NCX1\_1}
\label{fig:FIRE_FA2S1C1NCX1_1_BDP_A7}
\end{figure}

\begin{figure}[!ht]
\includegraphics[width=6in]{../Figures/Script_Figures/FIRE_FA2S1C1NCX1_1_TC_A7}
\caption{Temperature at exterior Door A, Test FIRE\_FA2S1C1NCX1\_1}
\label{fig:FIRE_FA2S1C1NCX1_1_TC_A7}
\end{figure}

\begin{figure}[!ht]
\includegraphics[width=6in]{../Figures/Script_Figures/FIRE_FA2S1C1NCX1_1_BDP_A8}
\caption{Velocity at exterior Door C\_West, Test FIRE\_FA2S1C1NCX1\_1}
\label{fig:FIRE_FA2S1C1NCX1_1_BDP_A8}
\end{figure}

\begin{figure}[!ht]
\includegraphics[width=6in]{../Figures/Script_Figures/FIRE_FA2S1C1NCX1_1_TC_A8}
\caption{Temperature at exterior Door C\_West, Test FIRE\_FA2S1C1NCX1\_1}
\label{fig:FIRE_FA2S1C1NCX1_1_TC_A8}
\end{figure}

\begin{figure}[!ht]
\includegraphics[width=6in]{../Figures/Script_Figures/FIRE_FA2S1C1NCX1_1_BDP_A9}
\caption{Velocity at exterior Door C\_East, Test FIRE\_FA2S1C1NCX1\_1}
\label{fig:FIRE_FA2S1C1NCX1_1_BDP_A9}
\end{figure}

\begin{figure}[!ht]
\includegraphics[width=6in]{../Figures/Script_Figures/FIRE_FA2S1C1NCX1_1_TC_A9}
\caption{Temperature at exterior Door C\_East, Test FIRE\_FA2S1C1NCX1\_1}
\label{fig:FIRE_FA2S1C1NCX1_1_TC_A9}
\end{figure}

\begin{figure}[!ht]
\includegraphics[width=6in]{../Figures/Script_Figures/FIRE_FA2S1C1NCX1_1_GAS}
\caption{Gas Concentration, Test FIRE\_FA2S1C1NCX1\_1}
\label{fig:FIRE_FA2S1C1NCX1_1_GAS}
\end{figure}

\begin{figure}[!ht]
\includegraphics[width=6in]{../Figures/Script_Figures/FIRE_FA2S1C1NCX1_1_HF}
\caption{Heat Flux, Test FIRE\_FA2S1C1NCX1\_1}
\label{fig:FIRE_FA2S1C1NCX1_1_HF}
\end{figure}

\begin{figure}[!ht]
\includegraphics[width=6in]{../Figures/Script_Figures/FIRE_FA2S1C1NCX1_1_TC_A1}
\caption{Temperature at TC Tree A1, Room A, Test FIRE\_FA2S1C1NCX1\_1}
\label{fig:FIRE_FA2S1C1NCX1_1_TC_A1}
\end{figure}

\begin{figure}[!ht]
\includegraphics[width=6in]{../Figures/Script_Figures/FIRE_FA2S1C1NCX1_1_TC_A2}
\caption{Temperature at TC Tree A2, Room A, Test FIRE\_FA2S1C1NCX1\_1}
\label{fig:FIRE_FA2S1C1NCX1_1_TC_A2}
\end{figure}

\begin{figure}[!ht]
\includegraphics[width=6in]{../Figures/Script_Figures/FIRE_FA2S1C1NCX1_1_TC_A3}
\caption{Temperature at TC Tree A3, Room B, Test FIRE\_FA2S1C1NCX1\_1}
\label{fig:FIRE_FA2S1C1NCX1_1_TC_A3}
\end{figure}

\begin{figure}[!ht]
\includegraphics[width=6in]{../Figures/Script_Figures/FIRE_FA2S1C1NCX1_1_TC_A4}
\caption{Temperature at TC Tree A4, Room C, Test FIRE\_FA2S1C1NCX1\_1}
\label{fig:FIRE_FA2S1C1NCX1_1_TC_A4}
\end{figure}

\begin{figure}[!ht]
\includegraphics[width=6in]{../Figures/Script_Figures/FIRE_FA2S1C1NCX1_1_TC_A5}
\caption{Temperature at TC Tree A5, Room C, Test FIRE\_FA2S1C1NCX1\_1}
\label{fig:FIRE_FA2S1C1NCX1_1_TC_A5}
\end{figure}

\subsection{FIRE\_FA2S1C1NCX1\_2}

\begin{figure}[!ht]
\includegraphics[width=6in]{../Figures/Script_Figures/FIRE_FA2S1C1NCX1_2_BDP_A7}
\caption{Velocity at exterior Door A, Test FIRE\_FA2S1C1NCX1\_2}
\label{fig:FIRE_FA2S1C1NCX1_2_BDP_A7}
\end{figure}

\begin{figure}[!ht]
\includegraphics[width=6in]{../Figures/Script_Figures/FIRE_FA2S1C1NCX1_2_TC_A7}
\caption{Temperature at exterior Door A, Test FIRE\_FA2S1C1NCX1\_2}
\label{fig:FIRE_FA2S1C1NCX1_2_TC_A7}
\end{figure}

\begin{figure}[!ht]
\includegraphics[width=6in]{../Figures/Script_Figures/FIRE_FA2S1C1NCX1_2_BDP_A8}
\caption{Velocity at exterior Door C\_West, Test FIRE\_FA2S1C1NCX1\_2}
\label{fig:FIRE_FA2S1C1NCX1_2_BDP_A8}
\end{figure}

\begin{figure}[!ht]
\includegraphics[width=6in]{../Figures/Script_Figures/FIRE_FA2S1C1NCX1_2_TC_A8}
\caption{Temperature at exterior Door C\_West, Test FIRE\_FA2S1C1NCX1\_2}
\label{fig:FIRE_FA2S1C1NCX1_2_TC_A8}
\end{figure}

\begin{figure}[!ht]
\includegraphics[width=6in]{../Figures/Script_Figures/FIRE_FA2S1C1NCX1_2_BDP_A9}
\caption{Velocity at exterior Door C\_East, Test FIRE\_FA2S1C1NCX1\_2}
\label{fig:FIRE_FA2S1C1NCX1_2_BDP_A9}
\end{figure}

\begin{figure}[!ht]
\includegraphics[width=6in]{../Figures/Script_Figures/FIRE_FA2S1C1NCX1_2_TC_A9}
\caption{Temperature at exterior Door C\_East, Test FIRE\_FA2S1C1NCX1\_2}
\label{fig:FIRE_FA2S1C1NCX1_2_TC_A9}
\end{figure}

\begin{figure}[!ht]
\includegraphics[width=6in]{../Figures/Script_Figures/FIRE_FA2S1C1NCX1_2_GAS}
\caption{Gas Concentration, Test FIRE\_FA2S1C1NCX1\_2}
\label{fig:FIRE_FA2S1C1NCX1_2_GAS}
\end{figure}

\begin{figure}[!ht]
\includegraphics[width=6in]{../Figures/Script_Figures/FIRE_FA2S1C1NCX1_2_HF}
\caption{Heat Flux, Test FIRE\_FA2S1C1NCX1\_2}
\label{fig:FIRE_FA2S1C1NCX1_2_HF}
\end{figure}

\begin{figure}[!ht]
\includegraphics[width=6in]{../Figures/Script_Figures/FIRE_FA2S1C1NCX1_2_TC_A1}
\caption{Temperature at TC Tree A1, Room A, Test FIRE\_FA2S1C1NCX1\_2}
\label{fig:FIRE_FA2S1C1NCX1_2_TC_A1}
\end{figure}

\begin{figure}[!ht]
\includegraphics[width=6in]{../Figures/Script_Figures/FIRE_FA2S1C1NCX1_2_TC_A2}
\caption{Temperature at TC Tree A2, Room A, Test FIRE\_FA2S1C1NCX1\_2}
\label{fig:FIRE_FA2S1C1NCX1_2_TC_A2}
\end{figure}

\begin{figure}[!ht]
\includegraphics[width=6in]{../Figures/Script_Figures/FIRE_FA2S1C1NCX1_2_TC_A3}
\caption{Temperature at TC Tree A3, Room B, Test FIRE\_FA2S1C1NCX1\_2}
\label{fig:FIRE_FA2S1C1NCX1_2_TC_A3}
\end{figure}

\begin{figure}[!ht]
\includegraphics[width=6in]{../Figures/Script_Figures/FIRE_FA2S1C1NCX1_2_TC_A4}
\caption{Temperature at TC Tree A4, Room C, Test FIRE\_FA2S1C1NCX1\_2}
\label{fig:FIRE_FA2S1C1NCX1_2_TC_A4}
\end{figure}

\begin{figure}[!ht]
\includegraphics[width=6in]{../Figures/Script_Figures/FIRE_FA2S1C1NCX1_2_TC_A5}
\caption{Temperature at TC Tree A5, Room C, Test FIRE\_FA2S1C1NCX1\_2}
\label{fig:FIRE_FA2S1C1NCX1_2_TC_A5}
\end{figure}

\subsection{FIRE\_FA2S1C1NCX1\_3}

\begin{figure}[!ht]
\includegraphics[width=6in]{../Figures/Script_Figures/FIRE_FA2S1C1NCX1_3_BDP_A7}
\caption{Velocity at exterior Door A, Test FIRE\_FA2S1C1NCX1\_3}
\label{fig:FIRE_FA2S1C1NCX1_3_BDP_A7}
\end{figure}

\begin{figure}[!ht]
\includegraphics[width=6in]{../Figures/Script_Figures/FIRE_FA2S1C1NCX1_3_TC_A7}
\caption{Temperature at exterior Door A, Test FIRE\_FA2S1C1NCX1\_3}
\label{fig:FIRE_FA2S1C1NCX1_3_TC_A7}
\end{figure}

\begin{figure}[!ht]
\includegraphics[width=6in]{../Figures/Script_Figures/FIRE_FA2S1C1NCX1_3_BDP_A8}
\caption{Velocity at exterior Door C\_West, Test FIRE\_FA2S1C1NCX1\_3}
\label{fig:FIRE_FA2S1C1NCX1_3_BDP_A8}
\end{figure}

\begin{figure}[!ht]
\includegraphics[width=6in]{../Figures/Script_Figures/FIRE_FA2S1C1NCX1_3_TC_A8}
\caption{Temperature at exterior Door C\_West, Test FIRE\_FA2S1C1NCX1\_3}
\label{fig:FIRE_FA2S1C1NCX1_3_TC_A8}
\end{figure}

\begin{figure}[!ht]
\includegraphics[width=6in]{../Figures/Script_Figures/FIRE_FA2S1C1NCX1_3_BDP_A9}
\caption{Velocity at exterior Door C\_East, Test FIRE\_FA2S1C1NCX1\_3}
\label{fig:FIRE_FA2S1C1NCX1_3_BDP_A9}
\end{figure}

\begin{figure}[!ht]
\includegraphics[width=6in]{../Figures/Script_Figures/FIRE_FA2S1C1NCX1_3_TC_A9}
\caption{Temperature at exterior Door C\_East, Test FIRE\_FA2S1C1NCX1\_3}
\label{fig:FIRE_FA2S1C1NCX1_3_TC_A9}
\end{figure}

\begin{figure}[!ht]
\includegraphics[width=6in]{../Figures/Script_Figures/FIRE_FA2S1C1NCX1_3_GAS}
\caption{Gas Concentration, Test FIRE\_FA2S1C1NCX1\_3}
\label{fig:FIRE_FA2S1C1NCX1_3_GAS}
\end{figure}

\begin{figure}[!ht]
\includegraphics[width=6in]{../Figures/Script_Figures/FIRE_FA2S1C1NCX1_3_HF}
\caption{Heat Flux, Test FIRE\_FA2S1C1NCX1\_3}
\label{fig:FIRE_FA2S1C1NCX1_3_HF}
\end{figure}

\begin{figure}[!ht]
\includegraphics[width=6in]{../Figures/Script_Figures/FIRE_FA2S1C1NCX1_3_TC_A1}
\caption{Temperature at TC Tree A1, Room A, Test FIRE\_FA2S1C1NCX1\_3}
\label{fig:FIRE_FA2S1C1NCX1_3_TC_A1}
\end{figure}

\begin{figure}[!ht]
\includegraphics[width=6in]{../Figures/Script_Figures/FIRE_FA2S1C1NCX1_3_TC_A2}
\caption{Temperature at TC Tree A2, Room A, Test FIRE\_FA2S1C1NCX1\_3}
\label{fig:FIRE_FA2S1C1NCX1_3_TC_A2}
\end{figure}

\begin{figure}[!ht]
\includegraphics[width=6in]{../Figures/Script_Figures/FIRE_FA2S1C1NCX1_3_TC_A3}
\caption{Temperature at TC Tree A3, Room B, Test FIRE\_FA2S1C1NCX1\_3}
\label{fig:FIRE_FA2S1C1NCX1_3_TC_A3}
\end{figure}

\begin{figure}[!ht]
\includegraphics[width=6in]{../Figures/Script_Figures/FIRE_FA2S1C1NCX1_3_TC_A4}
\caption{Temperature at TC Tree A4, Room C, Test FIRE\_FA2S1C1NCX1\_3}
\label{fig:FIRE_FA2S1C1NCX1_3_TC_A4}
\end{figure}

\begin{figure}[!ht]
\includegraphics[width=6in]{../Figures/Script_Figures/FIRE_FA2S1C1NCX1_3_TC_A5}
\caption{Temperature at TC Tree A5, Room C, Test FIRE\_FA2S1C1NCX1\_3}
\label{fig:FIRE_FA2S1C1NCX1_3_TC_A5}
\end{figure}

>>>>

\headerB{
Spartanburg 2014
}

@@

\subsection{Construction}
\label{sec:Construction}

@@

@@
